The limits of self commitment and private paternalism \thanks{}

### 2022-10-03 Tables/Attrition.tex
update of results using corrected deinition of apr

% Table generated by Excel2LaTeX from sheet 'Attrition'
\begin{tabular}{lcccccccc}
\toprule
      &       & \multicolumn{3}{c}{Commitment arms} &       & \multicolumn{3}{c}{Soft arms} \\
\cmidrule{3-5}\cmidrule{7-9}      & Control & Forced & Choice & p-value &       & Forced & Choice  & p-value \\
\midrule
\midrule
Number of branch-day pawns & 31    & 31    & 37    & 0.16  &       & 32    & 34    & 0.57 \\
      & (2.2) & (2.3) & (2.6) &       &       & (2.4) & (1.8) &  \\
Survey response rate & 0.77  & 0.75  & 0.77  & 0.74  &       & 0.8   & 0.79  & 0.5 \\
      & (0.02) & (0.03) & (0.02) &       &       & (0.02) & (0.02) &  \\
\% ended up pawning & 0.98  & 0.97  & 0.98  & 0.43  &       & 0.99  & 0.99  & 0.49 \\
      & (0.004) & (0.007) & (0.006) &       &       & (0.003) & (0.003) &  \\
\midrule
Obs   & 2600  & 2484  & 3435  &       &       & 2157  & 2768  &  \\
\bottomrule
\bottomrule
\end{tabular}%

>>>>

% Table generated by Excel2LaTeX from sheet 'Attrition'
\begin{tabular}{lcccccccc}
\toprule
      &       & \multicolumn{3}{c}{Commitment arms} &       & \multicolumn{3}{c}{Soft arms} \\
\cmidrule{3-5}\cmidrule{7-9}      & Control & Forced & Choice & p-value &       & Forced & Choice  & p-value \\
\midrule
\midrule
Number of branch-day pawns & 31    & 33    & 40    & 0.14  &       & 33    & 34    & 0.76 \\
      & (3)   & (2.7) & (3.3) &       &       & (3.2) & (2.2) &  \\
Survey response rate & 0.78  & 0.75  & 0.77  & 0.59  &       & 0.8   & 0.81  & 0.69 \\
      & (0.02) & (0.03) & (0.03) &       &       & (0.03) & (0.02) &  \\
\midrule
Obs   & 1770  & 1954  & 2580  &       &       & 1470  & 1904  &  \\
\bottomrule
\bottomrule
\end{tabular}%
